A tool set for random number generation on GPUs in R

### 2021-11-30 pkg/gpuRandom/inst/documents/paper1_2021_5/paper1.Rnw
change scale in colour plot
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@3017 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\documentclass[article]{jss}

@@

<<maternplot, echo=FALSE, eval=TRUE, cache=FALSE, dev='png', out.width = '0.47\\textwidth', fig.height=3, fig.width=4.5, fig.cap="Simulated Gaussian random fields", fig.subcap = theSubcap, fig.align='default'>>=
myCol = mapmisc::colourScale(breaks=c(-10, -5, seq(-3, 3), 5, 10), style='fixed', col='Spectral')
for(D in names(simRaster)) {
  mapmisc::map.new(simRaster)
  plot(simRaster[[D]], legend=FALSE, add=TRUE, col=myCol$col, breaks=myCol$breaks)
  plot(swissBorder, add=TRUE)
}
mapmisc::legendBreaks("right", myCol, inset=0)
@

>>>>

\documentclass[article,nojss]{jss}

@@

<<maternplot, echo=FALSE, eval=TRUE, cache=FALSE, dev='png', out.width = '0.47\\textwidth', fig.height=3, fig.width=4.5, fig.cap="Simulated Gaussian random fields", fig.subcap = theSubcap, fig.align='default'>>=
myCol = mapmisc::colourScale(breaks=sort(unique(c(-6, -4, seq(-2, 2), 4, 6))), style='fixed', col='Spectral')
for(D in names(simRaster)) {
  mapmisc::map.new(simRaster)
  plot(simRaster[[D]], legend=FALSE, add=TRUE, col=myCol$col, breaks=myCol$breaks)
  plot(swissBorder, add=TRUE)
}
mapmisc::legendBreaks("right", myCol, inset=0)
@
